WORKING TITLE: The adaptive value of green nest material across birds: A systematic review and meta-analysis

### 2025-05-11 docs/manuscript_GNM.qmd
Results for meta-regressions completed

```{r Setup, include=FALSE, echo=FALSE}
devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
pacman::p_load(readr,tidyverse,metafor,orchaRd,patchwork)

@@

```{r}
dataset_analysis <- read_csv("data/03_data_cleaning/dataset_analysis.csv")

@@

**Overall effect of green nest material on fitness proxies**

```{r}
intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))
bivariate_model<-readRDS(here::here("sensitivity_analysis/bivariate_model.rds"))
```

@@

The model using lnRR showed an average increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in green nest material \[@fig-mean-effect (A); lnRR = `{r} as.double(formatC(coef(intercept_lnRR), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_lnRR)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_lnRR)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_lnRR)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_lnRR)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_lnRR$pval, digits = 3, format = "f"))`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high. Total raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_lnRR$sigma2), 3)` (Q = `{r} round(sum(intercept_lnRR$QE),1)`, p \< 0.001), the measures of relative heterogeneity (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_lnRR)[1]),1)`%) and standardized heterogeneity metrics (CVH1~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_lnRR)[1]),2)` and M1~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_lnRR)[1]),2)`) suggested high variability across effect sizes. The model using SMDH showed a small positive and statistically significant effect of green nest material on fitness \[@fig-mean-effect (B) ; SMDH = `{r} as.double(formatC(coef(intercept_SMDH), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_SMDH)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_SMDH)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_SMDH)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_SMDH)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_SMDH$pval, digits = 3, format = "f"))`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], and heterogeneity among effect sizes was moderate to high. Raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_SMDH$sigma2), 3)` (Q = `{r} round(sum(intercept_SMDH$QE),1)`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_SMDH)[1]),1)`%) and the standardized heterogeneity metrics (CV~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_SMDH)[1]),2)` and M~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_SMDH)[1]),2)`) were moderately high (50th to 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution; @yang2023; see @supp-tab-heterogeneity for detailed estimates of heterogeneity)

@@

**Mechanisms behind green nest material effects**

```{r}
lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
SMDH_hypothesis<-readRDS(here::here("model/SMDH_hypothesis.rds"))
```

Using the multilevel meta-regressions with hypothesis type as a moderator, we found no clear support for either of the proposed mechanism [@fig-hypothesis]. There was a small positive but non-significant effect of green nest material on reproductive success in parents (courtship hypothesis) \[lnRR~courtship~ = `{r} as.double(formatC(coef(lnRR_hypothesis)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_hypothesis$pval[2], digits = 3, format = "f"))` and SMDH~courtship~ = `{r} as.double(formatC(coef(SMDH_hypothesis)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_hypothesis$pval[2], digits = 3, format = "f"))`\]. We found even smaller, non-significant effect of green nest material on protective effect or overall health benefits for the nestling as suggested by nest protection and drug hypothesis \[lnRR~parental_care~ = `{r} as.double(formatC(coef(lnRR_hypothesis)[3], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_hypothesis$pval[3], digits = 3, format = "f"))` and SMDH~parental_care~ = `{r} as.double(formatC(coef(SMDH_hypothesis)[3], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_hypothesis$pval[3], digits = 3, format = "f"))`\]. In case of the third category, both, that included the fitness proxies that could not be clearly assigned to either mechanisms, we found a small positive effect \[lnRR~both~ = `{r} as.double(formatC(coef(lnRR_hypothesis)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_hypothesis$pval[1], digits = 3, format = "f"))` and SMDH~both~ = `{r} as.double(formatC(coef(SMDH_hypothesis)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_hypothesis$pval[1], digits = 3, format = "f"))`\]. The moderator explained very little heterogeneity ($R^2~marginal$ for lnRR = `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and ($R^2~marginal$ for SMDH = `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).

![There is no clear evidence to favour either the courtship hypothesis or the parental care hypothesis as drivers of fitness benefits from green nest material in nests. Orchard plot of the multilevel meta-regression for A. log response ratio (lnRR) and B. Standardised mean difference (SMDH). Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error). k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_hypothesis.png){#fig-hypothesis width="1035"}

@@

```{r}
# Loading models for experimental design
lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))

# Loading models for parasite type
lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))

@@

There was no evidence that the effect of green nest material on parasite or pathogen load differed between arthropods and micro-organisms \[[@supp-fig-MR-non-sig]A-B; lnRR~arthropods~ = `{r} as.double(formatC(coef(lnRR_parasite)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_parasite$pval[1], digits = 3, format = "f"))` and SMDH~arthropods~ = `{r} as.double(formatC(coef(SMDH_parasite)[1], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_parasite$pval[1], digits = 3, format = "f"))`; lnRR~micro-organisms~ = `{r} as.double(formatC(coef(lnRR_parasite)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(lnRR_parasite$pval[2], digits = 3, format = "f"))` and SMDH~micro-organisms~ = `{r} as.double(formatC(coef(SMDH_parasite)[2], digit = 3, format="f"))` , p-value = `{r} as.double(formatC(SMDH_parasite$pval[2], digits = 3, format = "f"))`\]. The type of parasite or pathogen explained very little heterogeneity ($R^2~marginal$ for lnRR = `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2~marginal$ for SMDH = `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).

The meta-regression using bird species as a moderator showed no significantly different effect of green nest material on fitness depending on the bird being studied \[[@supp-fig-MR-non-sig]C-D\]; . However, it explained some heterogeneity in the effect sizes ($R^2~marginal$ for lnRR = `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2~marginal$ for SMDH = `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).

We explored the effect of green nest material on fitness depending on the type of trait studies (levels:physiology, morphology, reproduction, behaviour, parasite and pathogenic load, phenology) using a meta-regression with the trait type as a moderator.

To test the effect of time of addition of green nest material on the fitness outcome (levels: before egg hatching, after egg hatching, continuously throughout the nesting phase) we ran a meta-regression with Time of addition of green nest material as the moderator.

We explored the impact of methodological differences on the relationship between green nest material and fitness. To understand the effect of type of experimental design (i.e. whether the authors compared - non-aromatic vs. aromatic, no added material vs. aromatic, no added material vs. non-aromatic), we ran a meta-regression with type of experimental design as the moderator.

@@

![](figures/Figure_parasite_birds_trait.png){#supp-fig-MR-non-sig}

>>>>

```{r Setup, include=FALSE, echo=FALSE}
devtools::install_github("daniel1noble/orchaRd", ref = "main", force = TRUE)
pacman::p_load(readr,tidyverse,metafor,orchaRd,patchwork)
source(here::here("functions/extractor_metareg.R"))
```

@@

```{r review-results}
dataset_analysis <- read_csv("data/03_data_cleaning/dataset_analysis.csv")

@@

## **Overall effect of green nest material on fitness proxies**

```{r overall-results}
intercept_lnRR<-readRDS(here::here("model/intercept_lnRR.rds"))
intercept_SMDH<-readRDS(here::here("model/intercept_SMDH.rds"))
bivariate_model<-readRDS(here::here("sensitivity_analysis/bivariate_model.rds"))
```

@@

The model using lnRR showed an average increase in fitness of `{r} round((exp(as.double(coef(intercept_lnRR)))-1)*100,1)`% in nests with an experimental increase in green nest material \[@fig-mean-effect (A); lnRR = `{r} as.double(formatC(coef(intercept_lnRR), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_lnRR)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_lnRR)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_lnRR)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_lnRR)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_lnRR$pval, digits = 3, format = "f"))`, k = `{r} intercept_lnRR$k`, n = `{r} length(intercept_lnRR$s.levels.f[[1]])`\] but heterogeneity among effect sizes was high. Total raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_lnRR$sigma2), 3)` (Q = `{r} round(sum(intercept_lnRR$QE),1)`, p \< 0.001), the measures of relative heterogeneity (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_lnRR)[1]),1)`%) and standardized heterogeneity metrics (CVH2~total~ = `{r} round(as.double(orchaRd::cvh2_ml(intercept_lnRR)[1]),2)` and M2~total =~ `{r} round(as.double(orchaRd::m2_ml(intercept_lnRR)[1]),2)`) suggested high variability across effect sizes. The model using SMDH showed a small positive and statistically significant effect of green nest material on fitness \[@fig-mean-effect (B) ; SMDH = `{r} as.double(formatC(coef(intercept_SMDH), digits = 3, format = "f"))`, 95% CI: \[`{r} as.double(formatC((intercept_SMDH)$ci.lb, digits = 3, format = "f"))` to `{r} as.double(formatC((intercept_SMDH)$ci.ub, digits = 3, format = "f"))`\], 95% PI: \[`{r} as.double(formatC(predict(intercept_SMDH)$pi.lb, digits = 3, format = "f"))` to `{r} as.double(formatC(predict(intercept_SMDH)$pi.ub, digits = 3, format = "f"))`\], p-value = `{r} as.double(formatC(intercept_SMDH$pval, digits = 3, format = "f"))`, k = `{r} intercept_SMDH$k`, n = `{r} length(intercept_SMDH$s.levels.f[[1]])`\], and heterogeneity among effect sizes was moderate to high. Raw heterogeneity (𝜎^2^) was `{r} round(sum(intercept_SMDH$sigma2), 3)` (Q = `{r} round(sum(intercept_SMDH$QE),1)`, p \< 0.001), relative heterogeneity was substantially smaller compared to that of lnRR (I^2^~total~ = `{r} round(as.double(orchaRd::i2_ml(intercept_SMDH)[1]),1)`%) and the standardized heterogeneity metrics (CV~total~ = `{r} round(as.double(orchaRd::cvh1_ml(intercept_SMDH)[1]),2)` and M~total =~ `{r} round(as.double(orchaRd::m1_ml(intercept_SMDH)[1]),2)`) were moderately high (50th to 75th percentile of empirically derived estimates from meta-analyses in ecology and evolution; @yang2024a; see @supp-tab-heterogeneity for detailed estimates of heterogeneity)

@@

## **Hypotheses explaining the effect of green nest material**

```{r hypotheses-results}
lnRR_hypothesis<-readRDS(here::here("model/lnRR_hypothesis.rds"))
SMDH_hypothesis<-readRDS(here::here("model/SMDH_hypothesis.rds"))

summary_lnRR_hypothesis<-extractor_metareg(lnRR_hypothesis,"Hypothesis")
summary_SMDH_hypothesis<-extractor_metareg(SMDH_hypothesis,"Hypothesis")
```

Using the multilevel meta-regressions, we found no clear support for the proposed hypotheses in the literature ([@fig-hypothesis]). There is a small positive but non-significant effect of green nest material on fitness related to reproductive success in parents (courtship hypothesis) \[lnRR~courtship~ = `{r} summary_lnRR_hypothesis$estimate[2]`, CI: `{r} summary_lnRR_hypothesis$CI[2]`, PI: `{r} summary_lnRR_hypothesis$PI[2]`, p-value = `{r} summary_lnRR_hypothesis$p_value[2]`, k = `{r} summary_lnRR_hypothesis$k[2]`, n = `{r} summary_lnRR_hypothesis$n[2]` and SMDH~courtship~ = `{r} summary_SMDH_hypothesis$estimate[2]`, CI: `{r} summary_SMDH_hypothesis$CI[2]`, PI: `{r} summary_SMDH_hypothesis$PI[2]`, p-value = `{r} summary_SMDH_hypothesis$p_value[2]`, k = `{r} summary_SMDH_hypothesis$k[2]`, n = `{r} summary_SMDH_hypothesis$n[2]`\]. We found even smaller, non-significant effect of green nest material on fitness related to protective effect or overall health benefits for the nestling as suggested by nest protection and drug hypothesis \[lnRR~parental_care~ =`{r} summary_lnRR_hypothesis$estimate[3]`, CI: `{r} summary_lnRR_hypothesis$CI[3]`, PI: `{r} summary_lnRR_hypothesis$PI[3]`, p-value = `{r} summary_lnRR_hypothesis$p_value[3]`, k = `{r} summary_lnRR_hypothesis$k[3]`, n = `{r} summary_lnRR_hypothesis$n[3]` and SMDH~parental_care~ = `{r} summary_SMDH_hypothesis$estimate[3]`, CI: `{r} summary_SMDH_hypothesis$CI[3]`, PI: `{r} summary_SMDH_hypothesis$PI[3]`, p-value = `{r} summary_SMDH_hypothesis$p_value[3]`, k = `{r} summary_SMDH_hypothesis$k[3]`, n = `{r} summary_SMDH_hypothesis$n[3]`\]. In case of the third category, both, that included the fitness proxies that could not be clearly assigned to either hypotheses, we found a small positive effect which was significant only in the case of SMDH \[lnRR~both~ = `{r} summary_lnRR_hypothesis$estimate[1]`, CI: `{r} summary_lnRR_hypothesis$CI[1]`, PI: `{r} summary_lnRR_hypothesis$PI[1]`, p-value = `{r} summary_lnRR_hypothesis$p_value[1]`, k = `{r} summary_lnRR_hypothesis$k[1]`, n = `{r} summary_lnRR_hypothesis$n[1]` and SMDH~both~ = `{r} summary_SMDH_hypothesis$estimate[1]`, CI: `{r} summary_SMDH_hypothesis$CI[1]`, PI: `{r} summary_SMDH_hypothesis$PI[1]`, p-value = `{r} summary_SMDH_hypothesis$p_value[1]`, k = `{r} summary_SMDH_hypothesis$k[1]`, n = `{r} summary_SMDH_hypothesis$n[1]`\]. The moderator explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_hypothesis)*100,1))[1]`% and ($R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_hypothesis)*100,1))[1]`%).

![There is no clear evidence to favour either the courtship hypothesis or the parental care hypothesis as drivers of fitness benefits from green nest material in nests. Orchard plot of the multilevel meta-regression for A. log response ratio (lnRR) and B. Standardized mean difference (SMDH). Plots showing the mean estimates (large circles), 95% confidence intervals (thicker bars) and prediction intervals (thinner bars) and the individual data points (coloured circles) scaled by precision (inverse of standard error). k: number of effect sizes (number of studies is shown in the brackets).](figures/Figure_hypothesis.png){#fig-hypothesis width="1035"}

@@

```{r}
# Loading models for parasite type
lnRR_parasite<-readRDS(here::here("model/lnRR_parasite.rds"))
SMDH_parasite<-readRDS(here::here("model/SMDH_parasite.rds"))

summary_lnRR_parasite<-extractor_metareg(lnRR_parasite,"parasite_type")
summary_SMDH_parasite<-extractor_metareg(SMDH_parasite,"parasite_type")

summary_lnRR_birds<-extractor_metareg(lnRR_birds,"bird_species")
summary_SMDH_birds<-extractor_metareg(SMDH_birds,"bird_species")

summary_lnRR_trait<-extractor_metareg(lnRR_trait,"trait_type")
summary_SMDH_trait<-extractor_metareg(SMDH_trait,"trait_type")

@@

summary_lnRR_time_gnm_addition<- extractor_metareg(lnRR_time_gnm_addition,"time_of_gnm_addition")
summary_SMDH_time_gnm_addition<- extractor_metareg(SMDH_time_gnm_addition,"time_of_gnm_addition")

# Loading models for experimental design
lnRR_design<-readRDS(here::here("model/lnRR_design.rds"))
SMDH_design<-readRDS(here::here("model/SMDH_design.rds"))

summary_lnRR_design<- extractor_metareg(lnRR_design,"comparision_type")
summary_SMDH_design<- extractor_metareg(SMDH_design,"comparision_type")
```

The effect of green nest material on fitness varied largely by the experimental design. The experimental design comparison between no added material and aromatic material showed a positive and statistically significant effect on fitness \[[\@fig-MR](A-B); lnRR~no-material-vs-aromatic~ = `{r} summary_lnRR_design$estimate[2]`, CI: `{r} summary_lnRR_design$CI[2]`, PI: `{r} summary_lnRR_design$PI[2]`, p-value = `{r} summary_lnRR_design$p_value[2]`, k = `{r} summary_lnRR_design$k[2]`, n = `{r} summary_lnRR_design$n[2]` and SMDH~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[2]`, CI: `{r} summary_SMDH_design$CI[2]`, PI: `{r} summary_SMDH_design$PI[2]`, p-value = `{r} summary_SMDH_design$p_value[2]`, k = `{r} summary_SMDH_design$k[2]`, n = `{r} summary_SMDH_design$n[2]`\]. The experimental design comparison between no added material and non-aromatic material showed a negative effect on fitness, which was significant in lnRR \[lnRR~no-material-vs-non-aromatic~ = `{r} summary_lnRR_design$estimate[3]`, CI: `{r} summary_lnRR_design$CI[3]`, PI: `{r} summary_lnRR_design$PI[3]`, p-value = `{r} summary_lnRR_design$p_value[3]`, k = `{r} summary_lnRR_design$k[3]`, n = `{r} summary_lnRR_design$n[3]` and SMDH~no-material-vs-aromatic~ = `{r} summary_SMDH_design$estimate[3]`, CI: `{r} summary_SMDH_design$CI[3]`, PI: `{r} summary_SMDH_design$PI[3]`, p-value = `{r} summary_SMDH_design$p_value[3]`, k = `{r} summary_SMDH_design$k[3]`, n = `{r} summary_SMDH_design$n[3]`\]. Contrary to our expectation, the non-aromatic and aromatic green nest material comparison showed small negative non-significant effect on fitness \[lnRR~non-aromatic-vs-aromatic~ = `{r} summary_lnRR_design$estimate[1]`, CI: `{r} summary_lnRR_design$CI[1]`, PI: `{r} summary_lnRR_design$PI[1]`, p-value = `{r} summary_lnRR_design$p_value[1]`, k = `{r} summary_lnRR_design$k[1]`, n = `{r} summary_lnRR_design$n[1]` and SMDH~non-aromatic-vs-aromatic~ = `{r} summary_SMDH_design$estimate[1]`, CI: `{r} summary_SMDH_design$CI[1]`, PI: `{r} summary_SMDH_design$PI[1]`, p-value = `{r} summary_SMDH_design$p_value[1]`, k = `{r} summary_SMDH_design$k[1]`, n = `{r} summary_SMDH_design$n[1]`\]. Experimental design comparison type also explained a large proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_design)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_design)*100,1))[1]`%).

When green nest material was added continuously throughout the nesting phase, the effect of it on fitness was positive and statistically significant in the case of SMDH \[lnRR~continously~ =`{r} summary_lnRR_time_gnm_addition$estimate[3]`, CI: `{r} summary_lnRR_time_gnm_addition$CI[3]`, PI: `{r} summary_lnRR_time_gnm_addition$PI[3]`, p-value = `{r} summary_lnRR_time_gnm_addition$p_value[3]`, k = `{r} summary_lnRR_time_gnm_addition$k[3]`, n = `{r} summary_lnRR_time_gnm_addition$n[3]` and SMDH~continously~ = `{r} summary_SMDH_time_gnm_addition$estimate[3]`, CI: `{r} summary_SMDH_time_gnm_addition$CI[3]`, PI: `{r} summary_SMDH_time_gnm_addition$PI[3]`, p-value = `{r} summary_SMDH_time_gnm_addition$p_value[3]`, k = `{r} summary_SMDH_time_gnm_addition$k[3]`, n = `{r} summary_SMDH_time_gnm_addition$n[3]`\]. Addition after egg hatching showed a positive but non-significant effect on fitness and before egg hatching had a near zero non-significant effect [\@fig-MR](C-D); Table X\]. Timing of addition of green nest material explained a small proportion of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_time_gnm_addition)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_time_gnm_addition)*100,1))[1]`%).

![](figures/Figure_design_time_gnm_addition.png){#fig-MR}

There is positive non-significant effect of increased green nest material on fitness proxies relating to pathogen and parasitic load in case of arthropods and a negative non-significant effect in case of micro-organisms. \[[\@figsupp-MR](A-B); \[lnRR~arthropod~ = `{r} summary_lnRR_parasite$estimate[1]`, CI: `{r} summary_lnRR_parasite$CI[1]`, PI: `{r} summary_lnRR_parasite$PI[1]`, p-value = `{r} summary_lnRR_parasite$p_value[1]`, k = `{r} summary_lnRR_parasite$k[1]`, n = `{r} summary_lnRR_parasite$n[1]` and SMDH~arthropod~ = `{r} summary_SMDH_parasite$estimate[1]`, CI: `{r} summary_SMDH_parasite$CI[1]`, PI: `{r} summary_SMDH_parasite$PI[1]`, p-value = `{r} summary_SMDH_parasite$p_value[1]`, k = `{r} summary_SMDH_parasite$k[1]`, n = `{r} summary_SMDH_parasite$n[1]`; lnRR~mirco-organisms~ = `{r} summary_lnRR_parasite$estimate[2]`, CI: `{r} summary_lnRR_parasite$CI[2]`, PI: `{r} summary_lnRR_parasite$PI[2]`, p-value = `{r} summary_lnRR_parasite$p_value[2]`, k = `{r} summary_lnRR_parasite$k[2]`, n = `{r} summary_lnRR_parasite$n[2]` and SMDH~micro-organisms~ = `{r} summary_SMDH_parasite$estimate[2]`, CI: `{r} summary_SMDH_parasite$CI[2]`, PI: `{r} summary_SMDH_parasite$PI[2]`, p-value = `{r} summary_SMDH_parasite$p_value[2]`, k = `{r} summary_SMDH_parasite$k[2]`, n = `{r} summary_SMDH_parasite$n[2]`\]. The type of parasite or pathogen explained very little heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_parasite)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_parasite)*100,1))[1]`%).

Most bird species, showed a small positive non-significant increase it fitness with an experimental increase in green nest material, although some species showed negative but similarly non-significant effects \[[\@figsupp-MR](C-D); Table X\]. All confidence and prediction intervals overlapped zero. However, bird species identity explained a proportion of heterogeneity in the effect sizes ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_birds)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_birds)*100,1))[1]`%).

Among different types of fitness trait, only morphological trait showed positive effect of green nest material on fitness, which was statistically significant for SMDH \[lnRR~morphology~ = `{r} summary_lnRR_trait$estimate[2]`, CI: `{r} summary_lnRR_trait$CI[2]`, PI: `{r} summary_lnRR_trait$PI[2]`, p-value = `{r} summary_lnRR_trait$p_value[2]`, k = `{r} summary_lnRR_trait$k[2]`, n = `{r} summary_lnRR_trait$n[2]` and SMDH~morphology~ = `{r} summary_SMDH_trait$estimate[2]`, CI: `{r} summary_SMDH_trait$CI[2]`, PI: `{r} summary_SMDH_trait$PI[2]`, p-value = `{r} summary_SMDH_trait$p_value[2]`, k = `{r} summary_SMDH_trait$k[2]`, n = `{r} summary_SMDH_trait$n[2]`\]. Parasite and pathogen related fitness traits showed a small negative, non-significant effect in case of lnRR \[lnRR~parasite-pathogen~ = `{r} summary_lnRR_trait$estimate[3]`, CI: `{r} summary_lnRR_trait$CI[3]`, PI: `{r} summary_lnRR_trait$PI[3]`, p-value = `{r} summary_lnRR_trait$p_value[3]`, k = `{r} summary_lnRR_trait$k[3]`, n = `{r} summary_lnRR_trait$n[3]` and SMDH~parasite-pathogen~ = `{r} summary_SMDH_trait$estimate[3]`, CI: `{r} summary_SMDH_trait$CI[3]`, PI: `{r} summary_SMDH_trait$PI[3]`, p-value = `{r} summary_SMDH_trait$p_value[3]`, k = `{r} summary_SMDH_trait$k[3]`, n = `{r} summary_SMDH_trait$n[3]`\]. All other traits including behaviour, physiology, reproduction and phenology, showed small, non-significant effects [\@figsupp-MR](E-F); Table X\]. Trait type accounted for a small amount of heterogeneity ($R^2_{marginal(lnRR)}$= `{r} as.double(round(orchaRd::r2_ml(lnRR_trait)*100,1))[1]`% and $R^2_{marginal(SMDH)}$= `{r} as.double(round(orchaRd::r2_ml(SMDH_trait)*100,1))[1]`%).

## **Publication Bias**

@@

```{r results='asis'}
cat(readLines("tables/EA_MLMR_table.html"), sep ="\n")
```

![](figures/Figure_parasite_birds_trait.png){#figsupp-MR}
